\documentclass[a4paper,12pt]{article}
\usepackage[a4paper, total={180mm, 272mm}]{geometry}

\usepackage{fontspec}
\setmainfont[Path=fonts/, Extension=.ttf]{ipaexm}

\setlength\parindent{3.5em}
\setlength\parskip{0em}
\renewcommand{\baselinestretch}{1.247}

\begin{document}

\thispagestyle{empty}

\Large
\noindent \\
Level Master Ino\medskip
\par
\normalsize
Allows to perform a global correction to the image levels.\par
For adjusting levels individually on RGBA channels, use the \textquotedbl Level RGBA Ino\textquotedbl \ effect.\\
\\
-{-}- \ Inputs \ -{-}-\\
Source\par
Connect the image to be processed.\\
\\
Reference\par
Connect the reference image to assign the strength of the effect into each pixel.\\
\\
-{-}- \ Settings \ -{-}-\\
In\par
Allows to define the minimum and maximum values for the input pixel values.\par
Values less than Min will be limited to Min, values greater than Max will be\par 
limited to Max.\par
Minimum value is 0, maximum value is 1.\par
The default values are Min: 0, Max: 1.\par
Values can take an input of up to 4 decimal places.\\
\\
Out\par
Allows to fit the range defined by \textquotedbl In\textquotedbl , to the range of\par 
minimum and maximum values specified here.\par
Minimum value is 0, maximum value is 1.\par
The default values are, Min: 0, Max: 1.\par
Values can take an input of up to 4 decimal places.\\
\\
Gamma\par
Perform gamma correction between \textquotedbl Out Min\textquotedbl \ and \textquotedbl Out Max\textquotedbl .\par
A value between 0.1 and 1.0, will make the image become darker.\par
When the value is 1.0, no correction will be performed.\par
A value between 1.0 and 10.0, will make the image become brighter.\par
The default value is 1.\\
\\
Alpha Rendering\par
This option is valid only when there is an Alpha channel.\par
When inactive, it masks the changes in the RGB values using the original Alpha\par 
of the image.\par
When active, the effect will be able to modify the Alpha channel, extending it\par 
as necessary to reproduce the full span of the effect.\par
The default setting is ON.\\
\\
Premultiplied\par
When ON, the image will be processed as if having a Premultiplied Alpha channel\par 
(Alpha value already multiplied by RGB channels).\par
If image is not premultiplied, the image may not look correct.\par
The default setting is ON.\\
\\
Reference\par
Specify which channel to use from the image connected to the Reference port to\par 
drive the intensity of the effect.\par
Choose from Red/Green/Blue/Alpha/Luminance.\par
Choose Nothing to disable the effect.\par
The default value is \textquotedbl Red\textquotedbl .

\end{document}