\documentclass[a4paper,12pt]{article}
\usepackage[a4paper, total={180mm, 272mm}]{geometry}

\usepackage{fontspec}
\setmainfont[Path=fonts/, Extension=.ttf]{ipaexm}

\setlength\parindent{3.5em}
\setlength\parskip{0em}
\renewcommand{\baselinestretch}{1.247}

\begin{document}

\thispagestyle{empty}

\Large
\noindent \\
PN Clouds Ino\medskip
\par
\normalsize
Generates a cloud pattern image.\\
\par
pixel value,\par
\noindent \hskip 7em \ \ 8bits Image 128(0x80)\par
\noindent \hskip 7em 16bits Image 32768(0x8000)\par
Will be the center noise value.\par
It should be noted that this value is greater than the noise value\par
and a small value will not be necessarily be even.\\
\\
-{-}- \ Settings \ -{-}-\\
Size\par
Specify the size of the noise for the pattern.\par
Using a reduced value makes a small pattern, a bigger value makes a large pattern.\par
The unit is mm.\par
The default value is 10.\\
\\
Z\par
Continuously changes the image.\par
For example, from 1 to 24 frames it changes from 0 to 1.\par
The default value is 0.\\
\\
Octaves\par
Determine the detail of the cloud pattern.\par
Specify an integer from 1 to 10.\par
More detail in the noise will appear as the number increases.\par
The default value is 1.\\
\\
Persistance\par
Specify the strength of the details in the noise of the cloud pattern.\\
\\
Alpha Rendering\par
When OFF fill in the maximum Alpha value, over the entire surface will be opaque.\par
When ON it produces the same image as the RGB over the Alpha channel.\par
The default setting is ON.

\end{document}