\documentclass[a4paper,12pt]{article}
\usepackage[a4paper, total={180mm, 272mm}]{geometry}

\usepackage{fontspec}
\setmainfont[Path=fonts/, Extension=.ttf]{ipaexm}

\setlength\parindent{3.5em}
\setlength\parskip{0em}
\renewcommand{\baselinestretch}{1.247}

\begin{document}

\thispagestyle{empty}

\Large
\noindent \\
Soft Light Ino\medskip
\par
\normalsize
Soft Light the image.\par
A softened Hard Light effect.\par
Formula = if (Fore < 0.5) then\par
\noindent \hskip 7em (Back - (1 - 2 × Fore) × Back × (1 - Back))\par
\noindent \hskip 6em else\par
\noindent \hskip 7em if ((Back < 0.25) then\par
\noindent \hskip 10.5em (Back + (2 × Fore - 1) × (((16 × Back - 12) × Back + 4) × Back - Back))\par
\noindent \hskip 7em else\par
\noindent \hskip 10.5em (Back + (2 × Fore - 1) × (sqrt(Back) - Back)))\par
The formula results in each RGB value ranging from 0 to 1.\\
\\
-{-}- \ Inputs \ -{-}-\par
When both input ports are connected, they will be combined in the process.\par
When the node Visibility switch is OFF it will display the Back port content.\par
If there is only one port connected, it will display its content.\\
Fore\par
Connect the image that will be overlayed on top.\\
Back\par
Connect the base image.\\
\\
-{-}- \ Settings \ -{-}-\\
Opacity\par
Specifies the opacity of the image overlaid on top.\par
When 0 the Fore image will be transparent.\par
With the default value \textquotedbl 1.0\textquotedbl \ , the Fore image will be composed as opaque.\par
Specify a value from 0 to 1.0.\\
\\
Clipping Mask\par
When ON, it will take the Back port alpha information to define the alpha of the\par
resulting image, leaving areas where the Alpha value is zero as transparent.\par
The default value is ON.

\end{document}