\documentclass[a4paper,12pt]{article}
\usepackage[a4paper, total={180mm, 272mm}]{geometry}

\usepackage{fontspec}
\setmainfont[Path=fonts/, Extension=.ttf]{ipaexm}

\setlength\parindent{3.5em}
\setlength\parskip{0em}
\renewcommand{\baselinestretch}{1.247}

\begin{document}

\thispagestyle{empty}

\Large
\noindent \\
Warp HV Ino\medskip
\par
\normalsize
Distorts the image based on a reference image.\\
\\
-{-}- \ Inputs \ -{-}-\\
Source\par
Connect the image to be processed.\\
Hori\par
Connect a reference image to distort in the horizontal direction.\\
Vert\par
Connect a reference image to distort in the vertical direction.\\
\\
-{-}- \ Settings \ -{-}-\\
H reference\par
Allows to select which channel of the \textquotedbl Hori\textquotedbl \ image will drive the distorsion.\\
\\
H MaxLen\par
Distorts the picture in the horizontal direction.\par
Specify the maximum value of the distortion.\par
The unit is mm, values can range from 0 to 100.\par
Default value is 0, which will not make any effect.\\
\par
8bits Image\par
\noindent \hskip 7em \ \ \ \ 1 -MaxLen(mm) distorsion.\par
\noindent \hskip 7em 128 no distortion.\par
\noindent \hskip 7em 255 MaxLen(mm) distorsion.\par
16bits Image\par
\noindent \hskip 7em \ \ \ \ \ \ \ \ 1 -MaxLen(mm) distorsion.\par
\noindent \hskip 7em 32768 no distortion.\par
\noindent \hskip 7em 65535 MaxLen(mm) distorsion.\\
\\
V reference\par
Allows to select which channel of the \textquotedbl Vert\textquotedbl \ image will drive the distorsion.\\
\\
V MaxLen\par
Distorts the picture in the vertical direction.\par
Options are the same as \textquotedbl H MaxLen\textquotedbl .\\
\newpage

\thispagestyle{empty}

\ \vspace{-0.2em}
\\
Alpha Rendering\par
This option is valid only when there is an Alpha channel.\par
When inactive, it masks the changes in the RGB values using the original Alpha\par 
of the image.\par
When active, the effect will be able to modify the Alpha channel, extending it\par 
as necessary to reproduce the full span of the effect.\par
The default setting is ON.\\
\\
Anti Aliasing\par
When inactive, no antialiasing will be applied to the resulting image.\par
When active, it will process the picture to remove jagged edges.\par
The default setting is ON.

\end{document}